\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}

\newcommand{\resumeSubheading}[4]{
  \item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-20pt}
}

\newcommand{\resumeProjectHeading}[2]{
  \item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \small#1 & #2 \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\begin{document}

%----------HEADING----------
\begin{center}
  \textbf{\Huge \scshape Chanul Dandeniya} \\ \vspace{1pt}
  \small 347-626-6214 $|$
  \href{mailto:cdandeniya2@gmail.com}{cdandeniya2@gmail.com} $|$
  \href{https://www.linkedin.com/in/cdandeniya/}{\underline{LinkedIn}} $|$
  \href{https://cdandeniya.vercel.app}{\underline{cdandeniya.vercel.app}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Stony Brook University}{}{BS Computer Science and Applied Mathematics/Statistics \textbf{(GPA: 3.8/4.0)}}{Expected May 2027}
  \vspace{5pt}
  \resumeItemListStart
    \resumeItem{\textbf{Awards:} Dean's Merit Fund for Engineering, Dr. Peter Baigent Memorial Scholarship, Presidential Scholar}
    \resumeItem{\textbf{Activities:} Delta Sigma Pi (Professional Business Fraternity) \textbar\ Startup Exchange (SBU)}
  \resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{2pt}

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
  {{\textbf{OuterLabs Studio}} $|$ {\normalfont\textit{Lead Technical Product Manager}}}
  {Brooklyn, NY $|$ Aug 2023 -- Aug 2025}
  {}{}
\resumeItemListStart
  \resumeItem{Drove end-to-end delivery for 5+ client projects (\$5K--\$25K scope), owning requirements, roadmaps, and stakeholder communication from kickoff through launch.}
  \resumeItem{Reduced client rework by 20\% by introducing structured user stories, acceptance criteria, and definition-of-done frameworks across engineering and design handoffs.}
  \resumeItem{Managed delivery pipeline in \textbf{Jira} (Kanban), triaging incoming requests, maintaining prioritized backlogs, and unblocking engineers to improve sprint predictability.}
\resumeItemListEnd

\resumeSubheading
  {{\textbf{Amazon}} $|$ {\normalfont\textit{Software Engineering Apprentice}}}
  {Manhattan, NY $|$ Oct 2021 -- Oct 2024}
  {}{}
\resumeItemListStart
  \resumeItem{Coordinated release validation for 10+ major billing service deployments: authored smoke test checklists, managed go/no-go criteria, and led post-deployment verification with on-call engineers across 3 teams.}
  \resumeItem{Partnered with engineering leads to scope and plan a multi-quarter microservices migration for billing infrastructure, tracking milestones in sprint reviews and managing risk across a 12-engineer team.}
  \resumeItem{Drove \textbf{CI/CD} improvements in \textbf{Amazon CodePipeline}, coordinating \textbf{Blue/Green} deployment rollouts and reducing deployment-related incidents by 15\%.}
\resumeItemListEnd

\resumeSubheading
  {{\textbf{Kroll}} $|$ {\normalfont\textit{Technology Intern, Release Engineering}}}
  {Remote $|$ Jun 2026 -- Aug 2026}
  {}{}
\resumeItemListStart
  \resumeItem{Coordinated release validation for 20+ production deployments across 4 engineering teams, managing go/no-go criteria, stakeholder sign-offs, and post-deployment verification checklists.}
  \resumeItem{Standardized release runbook templates and escalation procedures, reducing ambiguity in incident response and cutting average time to resolution by 25\% for deployment-related issues.}
\resumeItemListEnd

\resumeSubheading
  {{\textbf{Saiera}} $|$ {\normalfont\textit{Software Development Intern}}}
  {Remote $|$ Jun 2025 -- Aug 2025}
  {}{}
\resumeItemListStart
  \resumeItem{Defined requirements and acceptance criteria for a multimodal study chatbot (GPT-4o), aligning weekly stakeholder reviews with development progress to hit launch milestones.}
  \resumeItem{Shipped document ingestion pipeline (S3, MongoDB) from spec to production, owning QA sign-off and monitoring post-launch performance metrics.}
\resumeItemListEnd

\resumeSubheading
  {{\textbf{Research Lab}} $|$ {\normalfont\textit{Lead Undergraduate Researcher}}}
  {Stony Brook, NY $|$ Jan 2025 -- May 2025}
  {}{}
\resumeItemListStart
  \resumeItem{Led a 4-person engineering team delivering a real-time activity recognition pipeline; ran weekly design reviews, owned sprint planning in \textbf{Jira}, and managed milestones to on-time delivery.}
\resumeItemListEnd

\resumeSubheading
  {{\textbf{TechCodes}} $|$ {\normalfont\textit{Founder \& Executive Director}}}
  {Brooklyn, NY $|$ 2020 -- 2023}
  {}{}
\resumeItemListStart
  \resumeItem{Founded and scaled a youth coding nonprofit to 1,500+ students globally; coordinated 15 team members, managed \$15K+ in sponsorships, and iterated programs based on attendee feedback to drive 35\% engagement growth.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
  {\textbf{Robotic Implant Center} $|$ \emph{Digital Strategy, UX, Frontend Delivery} $|$ \href{https://roboticimplantsnyc.com/}{\underline{Website}}}{}
\resumeItemListStart
  \resumeItem{Owned discovery and requirements with the client, translating goals into a sitemap, content plan, and execution checklist for design and development.}
  \resumeItem{Coordinated timeline and reviews across design, dev, and QA; launched with analytics and heatmaps and improved consultation CTA conversion by 15\% in the first 60 days.}
\resumeItemListEnd

\resumeProjectHeading
  {\textbf{SOROS Connect} $|$ \emph{Product Design, Design System, Prototyping} $|$ \href{https://www.shopsoros.com/}{\underline{Website}}}{}
\resumeItemListStart
  \resumeItem{Created a reusable design system with component requirements, states, and acceptance criteria; shipped 60+ components with accessibility and theming guidelines.}
  \resumeItem{Worked with stakeholders to unblock checkout and crypto-payment UX, delivering prototypes and handoff specs that reduced UI rework during implementation.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
    \textbf{Product \& Program Management}{: Roadmaps, PRDs, User Stories, Acceptance Criteria, Sprint Planning, Backlog Prioritization, Stakeholder Management, Risk Management} \\
    \textbf{Delivery Tools}{: Jira, Kanban/Agile, Cross-Functional Collaboration, Release Coordination, Confluence} \\
    \textbf{Technical}{: Python, Java, SQL; AWS, CI/CD, REST APIs, System Architecture} \\
    \textbf{Analytics}{: KPI Definition, Metrics Tracking, A/B Testing Concepts, Basic Data Analysis}
  }}
\end{itemize}

\end{document}
